\documentclass{beamer}
 
\usepackage[utf8]{inputenc}
\usepackage{minted}

\usetheme{Madrid}
\usecolortheme{beaver}
 
\title{An Introduction to \LaTeX}
\author{ACM}
\institute{New York University}
\date{2019}
 
\begin{document}

 
\frame{\titlepage}
 

\begin{frame}
\frametitle{Why the f*** does this exist?}
Most of us begin our word processing journey with huble intentions

\[
\text{\textbf{Get the thing typed!}}
\]

So why bother with \LaTeX?

\end{frame}


\begin{frame}
\frametitle{Why the f*** does this exist?}

\begin{enumerate}

    \item It's beautiful.

        \begin{itemize}
            \item \textit{Especially} for math.
            \item Try and find a paper on Arxiv not written in \LaTeX.
        \end{itemize}

    \item It was created by scientists, for scientists.

        \begin{itemize}
            \item Large and active community.
            \item Online support is readily found.
        \end{itemize}

    \item It's powerful; extremely rich package community.

\end{enumerate}

\end{frame}

\begin{frame}
\frametitle{Who's it for?}

\begin{enumerate}

    \item<1-> Created by scientists, for scientists.

        \begin{itemize}
            \item Journal articles and theses, with or without complex math
                notation.
            \item The technical publishing industry.
            \item Your professors when cooking up problem sets to torture you
                with.
        \end{itemize}

    \item<2-> Not a word processor.

        \begin{itemize}
            \item No spell check \footnote{Technically untrue, see ispell}.
            \item No complete control over formatting.
        \end{itemize}
    \item<3-> "You take care of writing, and we'll take care of presentation."

\end{enumerate}

\end{frame}

\begin{frame}
\frametitle{How does this work?}

\begin{enumerate}

    \item You specify the input in a source file.

        \begin{itemize}
            \item Vi/Vim, Emacs, Sublime, \dots
            \item TeXMaker, TeXStudio, \dots
        \end{itemize}

    \item LaTeX processes the content and decides how best to typeset it.

\end{enumerate}

\vspace{0.5cm}

\framebox[\linewidth]{\mintinline{latex}{I have a Latin test \textbf{tomorrow},
        but here I am \dots}}

\vspace{0.5cm}

\framebox[\linewidth]{I have a Latin test \textbf{tomorrow}, but here I am
    \dots}

\end{frame}
 
\end{document}
